---
title: "PIAU 2"
author: "Luís Romera"
format: html
editor: visual
---

## Objective

Let's try managing the data in a different way to fit the regression.

## Data manipulation

Let's try fitting through the **average values**, instead of the absolute values.

### HTR8

```{r}

library(magick)

setwd(
  "C:/Users/luisr/Documentos/Documents/Documentos - Copia/Projeto Thati/PIAU_Project"
  )

Havg <- read.csv(
  "Dados_westernblot_form_HTR8.csv"
  )

View(
  Havg
  )

head(
  Havg
  )
```

### Plotting the data

```{r}
#| message: false
#| warning: false
#| dev: png

Havg$conc <- as.character(
  Havg$conc
)

library(tidyverse)

ggplot(
  data = subset(
    Havg, tipo == "mean"
    )
) + 
  geom_point(
    mapping = aes(
      x = conc, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot HTR8",
    x = "Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

## Fitting the regression

### Endoglin

```{r}

Havg$conc <- as.numeric(
  Havg$conc
)

modelHE <- lm(
  exp ~ conc,
  data = Havg,
  subset = prot == "Endoglin" & tipo == "mean"
)

summary(
  modelHE
  )
```

The **regression** fitted to the expression of **endoglin** shows a **significant** angular coefficient very close to zero, but that is **negative** and could be interpreted as a **minor negative effect of the treatment**.

### PIGF

```{r}

modelHP <- lm(
  exp ~ conc,
  data = Havg,
  subset = prot == "PlGF" & tipo == "mean"
)

summary(
  modelHP
  )
```

**PIGF**, on the other side, shows **no significant coefficient** what could be interpreted as **lack of treatment effect**.

## BeWo

```{r}

Bavg <- read.csv(
  "Dados_westernblot_form_BeWo.csv"
)

View(
  Bavg
     )

head(
  Bavg
)
```

### Plotting the data

```{r}
#| dev: png
Bavg$conc <- as.character(
  Bavg$conc
)

ggplot(
  data = subset(
    Bavg, tipo == "mean"
    )
) + 
  geom_point(
    mapping = aes(
      x = conc, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot BeWo",
    x = "Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

## Fitting the regression

### Endoglin

```{r}

Bavg$conc <- as.numeric(
  Bavg$conc
)

modelBE <- lm(
  exp ~ conc,
  data = Bavg,
  subset = prot == "Endoglin" & tipo == "mean"
)

summary(
  modelBE
  )
```

In **BeWo** cells, there was **no significant angular coefficient for endoglin.**

### PIGF

```{r}

modelBP <- lm(
  exp ~ conc,
  data = Bavg,
  subset = prot == "PlGF" & tipo == "mean"
)

summary(
  modelBP
  )
```

**None for PIGF** either.

## Alternative

Analyzing the data, we may be facing a logarithmic relation, which could be affecting the linear regression.

Thus, let's try fitting through a logarithmic values first.

### HTR8

```{r}
Havg$log <- ifelse(
  Havg$conc > 0,
  log10(
    Havg$conc
  ),
  NA
)

#creating a log column, transforming Log0 in NAs

View(Havg)

head(Havg)
```

### Plotting the Data

```{r}
#| dev: png

ggplot(
  data = subset(
    Havg, tipo == "mean"
    )
) + 
  geom_point(
    mapping = aes(
      x = log, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot HTR8",
    x = "Log Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

Much smoother plot.

# Fitting the regression

### Endoglin

```{r}
modelHE <- lm(
  exp ~ log,
  data = Havg,
  subset = prot == "Endoglin" & tipo == "mean"
)

summary(
  modelHE
  )
```

### PIFG

```{r}
modelHP <- lm(
  exp ~ log,
  data = Havg,
  subset = prot == "PlGF" & tipo == "mean"
)

summary(
  modelHP
  )


```

```{r}
#| dev: png

#creating a new data frame with 100 values between the max and the min
#log value
visuHE <- data.frame( 
  log = seq(
    min(
      Havg$log[is.finite(
        Havg$log
      )]
    ),
    max(
      Havg$log[is.finite(
        Havg$log
      )]
    ),
    length.out = 100
  )
)

#Adding an expression response for each point based in the regression
visuHE$pred <- predict(
  modelHE,
  visuHE
)

View(visuHE)

visuHP <- data.frame(
  log = seq(
    min(
      Havg$log[is.finite(
        Havg$log
      )]
    ),
    max(
      Havg$log[is.finite(
        Havg$log
      )]
    ),
    length.out = 100
  )
)

visuHP$pred <- predict(
  modelHP,
  visuHP
)

#plotting the regression lines
ggplot(
  data = subset(
    Havg, tipo == "mean"
    )
) + 
  geom_line(
    data = visuHP,
    aes(
      x = log,
      y = pred
    ),
    color = "grey",
    linewidth = 1
  ) +
   geom_line(
    data = visuHE,
    aes(
      x = log,
      y = pred
    ),
    color = "grey",
    linewidth = 1
  ) +
  geom_point(
    mapping = aes(
      x = log, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot HTR8",
    x = "Log Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

## BeWo

```{r}
Bavg$log <- ifelse(
  Bavg$conc > 0,
  log10(
    Bavg$conc
  ),
  NA
)

#creating a log column, transforming Log0 in NAs

View(Bavg)

head(Bavg)
```

### Plotting the data

```{r}
#| dev: png

ggplot(
  data = subset(
    Bavg, tipo == "mean"
    )
) + 
  geom_point(
    mapping = aes(
      x = log, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot BeWo",
    x = "Log Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

## Fitting the regression

### Endoglin

```{r}
modelBE <- lm(
  exp ~ log,
  data = Bavg,
  subset = prot == "Endoglin" & tipo == "mean"
)

summary(
  modelBE
  )


```

### PIFG

```{r}
modelBP <- lm(
  exp ~ log,
  data = Bavg,
  subset = prot == "PlGF" & tipo == "mean"
)

summary(
  modelBP
  )
```

```{r}
modelBP <- lm(
  exp ~ log,
  data = Bavg,
  subset = prot == "PlGF" & tipo == "mean"
)

summary(
  modelBP
  )
```

```{r}
#| dev: png

visuBE <- data.frame(
  log = seq(
    min(
      Bavg$log[is.finite(
        Bavg$log
      )]
    ),
    max(
      Bavg$log[is.finite(
        Bavg$log
      )]
    ),
    length.out = 100
  )
)

visuBE$pred <- predict(
  modelBE,
  visuBE
)

visuBP <- data.frame(
  log = seq(
    min(
      Bavg$log[is.finite(
        Bavg$log
      )]
    ),
    max(
      Bavg$log[is.finite(
        Bavg$log
      )]
    ),
    length.out = 100
  )
)

visuBP$pred <- predict(
  modelBP,
  visuBP
)

ggplot(
  data = subset(
    Bavg, tipo == "mean"
    )
) + 
  geom_line(
    data = visuBP,
    aes(
      x = log,
      y = pred
    ),
    color = "grey",
    linewidth = 1
  ) +
   geom_line(
    data = visuBE,
    aes(
      x = log,
      y = pred
    ),
    color = "grey",
    linewidth = 1
  ) +
  geom_point(
    mapping = aes(
      x = log, y = exp, colour = prot
      ),
    size = 3
  ) +
  labs(
    title = "Western Blot BeWo",
    x = "Log Concentration (ug)",
    y = "Relative Expression",
    colour = "Protein"
  )
```

Analyzing now these data, **we acquired a significant angular coefficient for Endoglin on BeWo cells**. With the coefficient being positive, we shall discuss that the **treatment may cause a positive effect in the expression of Endoglin**.
