---
title: "PIAU"
author: "Luís Romera"
format: html
editor: visual
---

*This document is an attempt to work alternative statistics for the article **Cell-Type-Specific Immuno-Angiogenic Modulation in Trophoblasts by Curcumin Solid Lipid Nanoparticles.***

## The Data

First, let's take a look at the data:

We are working in the statistics of topic ***4.1 Modulation of Inflammation and Angiogenesis in Trophoblast Cells***.

Here, the authors measure the expression of two proteins:

-   **PIGF**

-   **Endoglin**

Through four groups, the **Control group** and other three groups of crescent concentrations:

-   **0.001**

-   **0.256**

-   **524.3**

And through two cell lines:

-   **HTR8/SVneo**

-   **BeWo**

```{r}
setwd("C:/Users/luisr/Documentos/Documents/Documentos - Copia/Projeto Thati/PIAU_Project") #moving to the files directory

dataWB <- read.csv("Dados_westernblot_form.csv") #Importing the data

View(dataWB) #visualizing the data
head(dataWB)

dataWB$conc <- as.character(dataWB$conc) #Changing concentration to character instead of double
```

Let's plot the data for some insights

```{r}
#| message: false
#| warning: false
#install.packages("tidyverse") #installing tidyverse for some visualization tools
library(tidyverse) #loading tidyverse

ggplot(data = dataWB) +
  geom_point(mapping = aes(x = conc, y = exp, colour = prot), 
             size = 3)
```


## Original Statistics

In the original statistics, it was performed an *ANOVA* test between control and concentration groups, for the two proteins and cell lines, which did not performed significantly.

## Alternative statistics

Now what I'm going to do is try an alternative statistic, involving fitting a **regression line** trough the data and trying to prove that the angular coefficient is significantly different than zero.
