---
title: "PIAU"
author: "Luís Romera"
format: pdf
editor: visual
---

*This document is an attempt to work alternative statistics for the article **Cell-Type-Specific Immuno-Angiogenic Modulation in Trophoblasts by Curcumin Solid Lipid Nanoparticles.***

## The Data

First, let's take a look at the data:

We are working in the statistics of topic ***4.1 Modulation of Inflammation and Angiogenesis in Trophoblast Cells***.

Here, the authors measure the expression of two proteins:

-   **PIGF**

-   **Endoglin**

Through four groups, the **Control group** and other three groups of crescent concentrations:

-   **0.001**

-   **0.256**

-   **524.3**

And through two cell lines:

-   **HTR8/SVneo**

-   **BeWo**

```{r}
#install.packages("magick")
library(magick)
setwd(
  "C:/Users/luisr/Documentos/Documents/Documentos - Copia/Projeto Thati/PIAU_Project"
  ) #moving to the file's directory

dataWB_HTR8 <- read.csv(
  "Dados_westernblot_form_HTR8.csv"
  ) #Importing the data

View(
  dataWB_HTR8
  ) #visualizing the data
head(
  dataWB_HTR8
  )

dataWB_HTR8$conc <- as.character(
  dataWB_HTR8$conc
  ) #Changing concentration to character instead of double so we can plot smoother 
```

### HTR8

We shall begin with **HTR8** cells

Let's plot the data for some insights

```{r}
#| message: false
#| warning: false
#| dev: png
#install.packages("tidyverse") #installing tidyverse for some visualization tools
library(
  tidyverse
  ) #loading tidyverse

ggplot(
   data = dataWB_HTR8
  ) +
  geom_point(
    mapping = aes(
      x = conc, y = exp, colour = prot
      ), 
             size = 3
    ) +
  labs(
    title = "Western Blot HTR8",
    x = "Dose Concentration (ug)",
    y = "Relative Protein Expression",
    color = "Protein"
  )
```

## Original Statistics

In the original statistics, it was performed an *ANOVA* test between control and concentration groups, for the two proteins and cell lines, which did not performed significantly.

In my perception, the data has a correlation, so measuring the difference between groups (such as using ANOVA) may hide this behavior.

## Alternative statistics

Now what I'm going to do is try an alternative statistic, involving fitting a **regression line** trough the data and trying to prove that the angular coefficient is significantly different than zero.

```{r}
#Let's change concentration back to "numeric" so we can do some calculations
dataWB_HTR8$conc <- as.numeric(
  dataWB_HTR8$conc
)

#Let's see if it worked
head(dataWB_HTR8)
```


```{r}
#Now lets try fitting a regression

#first, for Endoglin
EndHTR8 <- lm(
  exp ~ conc,
  data = dataWB_HTR8,
  subset = prot == "Endoglin"
)

#Let's see if it worked
summary(
  EndHTR8
  )

```

So, for **Endoglin**, the variance of the linear regression **does not** vary significantly from a line with an angular coefficient of zero.

```{r}
#Now, let's see for PIGF
PIGFHTR8 <- lm(
  exp ~ conc,
  data = dataWB_HTR8,
  subset = prot == "PlGF"
)

tail(
  dataWB_HTR8$prot
  ) #checking the name in the dataframe, something happened in the importation

#Let's see the results

summary(
  PIGFHTR8
  )

```

We achieved the **same** result with **PIGF**.

### BeWo

Now, let's try with **BeWo** cells

```{r}
#First, let's import the data

dataWB_BeWo <- read.csv(
  "Dados_westernblot_form_BeWo.csv"
)

#Let's view the data
View(
  dataWB_BeWo
  )

head(
  dataWB_BeWo
  )
```

Now, let's visualize the data

```{r}
#transforming conc from db to chr
dataWB_BeWo$conc <- as.character(
  dataWB_BeWo$conc
)

#see if it worked
head(
  dataWB_BeWo
)
```
And, finally, plot for insights

```{r}
#| dev: png
ggplot(
  data = dataWB_BeWo
    ) + 
  geom_point(
    mapping = aes(
      x = conc,
      y = exp,
      colour = prot
    ),
    size = 3
  ) +
  labs(
    title = "Western Blot BeWo",
    x = "Dose concentration (ug)",
    y = "Relative Protein Expression",
    color = "Protein"
  )
```

A nicer distribution, right?

Let's fit our regression

```{r}
#Changing conc back to db
dataWB_BeWo$conc <- as.numeric(
  dataWB_BeWo$conc
)

head(
  dataWB_BeWo
  )
```
Everything fine

```{r}
BewoEnd <- lm(
  exp ~ conc,
  data = dataWB_BeWo,
  subset = prot == "Endoglin"
)

summary(
  BewoEnd
)
```
```{r}
BewoPIGF <- lm(
  exp ~ conc,
  data = dataWB_BeWo,
  subset = prot == "PlGF"
)

summary(
  BewoPIGF
)
```

Summarizing, **none of the expressions varied in such a way that fitting a regression would achieve an angular coefficient significantly different than zero.**